% Cover letter using letter.sty
\documentclass{letter} % Uses 10pt
%Use \documentstyle[newcent]{letter} for New Century Schoolbook postscript font
% the following commands control the margins:
\topmargin=-1in    % Make letterhead start about 1 inch from top of page 
\textheight=10in  % text height can be bigger for a longer letter
\oddsidemargin=0pt % leftmargin is 1 inch
\textwidth=6.5in   % textwidth of 6.5in leaves 1 inch for right margin

\begin{document}

\signature{Nathan W Wynn}           % name for signature 
\longindentation=0pt                       % needed to get closing flush left
\let\raggedleft\raggedright                % needed to get date flush left
 
 
%\begin{letter}%{Ms. Terri Roberts \\
%Senior Staff Recruiter \\
%XYZ Corporation \\
%Rt. 56 \\
%Anytown, New Jersey 05867}


\begin{flushleft}
{\large\bf Nathan W Wynn}
\end{flushleft}
\medskip\hrule height 1pt
\begin{flushright}
\hfill 1256 Bethlehem Rd, Statham, GA 30666 \\
\hfill (762) 436-9384
\end{flushright} 
\vfill % forces letterhead to top of page

 
\opening{To Whom it ,} 
%Who are you? What are the most compelling reasons you can give for the admission committee
%to be interested in you? Sometimes they are looking for personal interests ? something that
%provides a little window into who you are as a person. Have there been any hardships that you
%have overcome? (Are you an underrepresented group? Attending a liberal arts college with
%limited research opportunities, first in your family to attend college, low income, rural, minority?
%Any of these classifications may help in your essay.)
\noindent My name is Nathan Wynn; I'm an undergraduate Computer Science student with a minor in Spanish at the University of Georgia. I'm interested in the REU program offered by the College of Staten Island. Throughout my academic career, I have excelled in all of my Computer Science courses, and I have also had the opportunity to further my studies outside of the realm of Computer Science by minoring in Spanish and taking 3D modeling and animation courses. After taking many rigorous upper level Computer Science courses, I have found a passion for tackling difficult problems and furthering my own understanding of the subject.

%\noindent Why are you interested in the subject area - What projects are you interested in?
%( Describe any personal, professional, or educational experiences that have contributed to your
%interest in the subject.)
\noindent I became interested in Computer Science in my Freshman year when I had the opportunity to take Discrete Mathematics and an introductory Computer Science course. I immediately knew that this was the right field for me, and since then I have sought out avenues to further my knowledge. During the summer of 2017, I had the opportunity to collaborate with Turner Broadcasting System as a Strategic Product Management Intern. During my internship, I collaborated with engineers, designers, and executives across the different Turner brands to invent new ways to spark innovation and research cutting edge technology solutions to provide benefit to Turner. This internship gave me the unique experience to witness the implementation, delivery, and research processes from a high level, and gave me a heightened passion for research within the realm of technology.


%\noindent What are your career goals? (This might also include your background, challenges,
%aspirations.)
\noindent After I graduate from the University of Georgia, I plan on attending graduate school. I am interested in many subfields of Computer Science, such as computing theory, graphics, human centered computing, human computer interaction, artificial intelligence, image processing, and modeling/simulation. I believe that pursuing my Masters degree will focus my interest by giving me more exposure to different research areas. After my Masters, I aspire to pursue a Doctorate degree and do research in either academia or with a research team in the corporate sector.


%\noindent What is your academic preparation? (Include relevant coursework, lab work, projects, etc. -
%you might describe an exciting or interesting experience you had in that subject area ? a course, a
%project, etc ? that peaked your interest.)
%\noindent To date, I have taken the following relevant courses: Algorithms, Data Structures, Computing Theory, Discrete Mathematics, Systems Programming, Software Development, Computer Architecture, and Computer Graphics - all of which I achieved high marks in. I am currently enrolled in Computer Networks and Virtual Reality.


\noindent In addition to my critical thinking and programming skills, I have strong written and verbal communication skills, which were strengthened by my positions as a Teaching Assistant at UGA and as an Intern at Turner Broadcasting System, where I presented my research in front of executives and the CTO at the end of the program. I also posses skills in presentation, user engagement, coordination, teaching, and conflict-resolution.
%What skills do you possess? Do you have any previous research experience? ? Describe
%previous research experience - this can include the following: undergraduate research, summer
%or part-time employment ? describe your role, did you perform research independently or as part
%of a team? What did you learn from your experience?


\noindent I believe that this REU program will aid me in my academic goals. This program will give me greater insight into different disciplines of Computer Science, and give me more exposure to cutting edge research. I am passionate about collaborating with others in defining and solving difficult problems. One of the past projects through this program that I was particularly interested in was "Parallel hash collision search by rho method with distinguished points" by Brian Weber (Univ. of Maryland at Baltimore County) and Samantha Morris (Univ. of Central Florida) under Dr. Xiaowen Zhang. I am particularly interested in the applications of the Birthday Paradox in increasing the probability of finding hash collisions.
%\noindent Why do you want to apply to this particular REU site? Why should the program be interested
%in you and why are you interested in us? What is interesting about the research? If they are
%researching Bees than you want to show interest in Bees. (For example, you should look at the
%REU web site to get an idea of what other students have done in the past, and then mention in
%your essay what mentors and topics are of primary and secondary interest to you.) 

\closing{Sincerely,} 
 

 
%\encl{}  				% Enclosures

\end{letter}
 

\end{document}






